---
title: "2024 Job Fair Recap"
output: 
pdf_document:
---

```{r setup, include=FALSE}
if (requireNamespace("thematic")) 
  thematic::thematic_rmd(font = "auto")

source(here::here('Master.R'))
df2
```

## Executive Summary

The 2024 Job Fair series, held throughout the year, successfully connected employers with job seekers across various industries. Key highlights include:

Number of Employers: A total of `r sum(df2$employer)` employers participated, offering a wide range of job opportunities.

Number of Job Seekers: The series attracted `r sum(df2$job_seekers)` job seekers, engaging in interviews and networking with potential employers.

Job Offers Extended: `r sum(df2$job_offers` job offers were made during the events, reflecting strong employer interest.

Follow-up Interviews: `r sum(df2$follow_up_interview)` follow-up interviews were scheduled, showing continued interest from employers in qualified candidates.

Overall, the 2024 Job Fair series was a highly effective platform for connecting talent with opportunities, driving job placements and ongoing recruitment.



 and 


## Themed Plots {.tabset .tabset-pills}

When running this document with [`{thematic}`](https://rstudio.github.io/thematic/) installed, the `thematic::thematic_rmd(font = "auto")` effectively translates `theme` (CSS) settings to new global theming defaults for `{ggplot2}`, `{lattice}`, and `{base}` R graphics:

### ggplot2

```{r,echo=FALSE, warning=FALSE,message=FALSE}
library(ggplot2)

ggplot(mpg, aes(displ, hwy)) +
  geom_point() + geom_smooth()
```

### lattice

```{r,echo=FALSE, warning=FALSE,message=FALSE}
lattice::show.settings()
```

### base

```{r,echo=FALSE, warning=FALSE,message=FALSE}
plot(pressure, col = thematic::thematic_get_option("accent"))
```


### test
```{r,echo=FALSE, warning=FALSE,message=FALSE}
source(here::here('Master.r'))

plot(employer)
```

