---
title: "Untitled"
output: html_document
date: "2025-01-08"
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r,include = FALSE, echo=FALSE, warning=FALSE,message=FALSE}
source(here::here('Master.R'))
df2
```

## Executive Summary

The 2024 Job Fair series, held throughout the year, successfully connected employers with job seekers across various industries. Key highlights include:

Number of Employers: A total of **`r sum(df2$employer)`** employers participated, offering a wide range of job opportunities.

Number of Job Seekers: The series attracted **`r sum(df2$job_seekers)`** job seekers, engaging in interviews and networking with potential employers.

Job Offers Extended: **`r sum(df2$job_offer)`** job offers were made during the events, reflecting strong employer interest.

Follow-up Interviews: **`r sum(df2$follow_up_interview)`** follow-up interviews were scheduled, showing continued interest from employers in qualified candidates.

Overall, the 2024 Job Fair series was a highly effective platform for connecting talent with opportunities, driving job placements and ongoing recruitment.
$$\\[1in]$$

```{r,echo=FALSE, warning=FALSE,message=FALSE}
df3 %>%
  gt_theme_nytimes() %>%
  gt_highlight_rows(rows = Event %in% c("LEDA Job Fair"),
                    fill = "steelblue" )

```

$$\\[1in]$$





## Plots {.tabset .tabset-pills}



### Employers

```{r,echo=FALSE, warning=FALSE,message=FALSE}
plot(employer)
```

### Job Seekers

```{r,echo=FALSE, warning=FALSE,message=FALSE}
plot(jobseeker)
```

### Job Offers

```{r,echo=FALSE, warning=FALSE,message=FALSE}
plot(joboffer)
```


### Follow Up
```{r,echo=FALSE, warning=FALSE,message=FALSE}
source(here::here('Master.r'))

plot(follow_up)
```

### Pie Chart

```{r,echo=FALSE, warning=FALSE,message=FALSE}
plot(pie)


```

